### 2021-06-22 src/paper/report.tex

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December onwards. Some states started
opening them gradually in late February, but operation at normal capacity did not resume
until the beginning of June. Figure~\ref{fig:school_scenarios} shows the effects of
different policies regarding school starting at Easter, at which point rapid tests had
become widely available. We estimate the realized scenario to have essentially the same
effect as a situation with closed schools. Under fully opened schools with mandatory
tests, total infections would have been 6\% higher; this number rises to 20\% without
tests. These effect sizes are broadly in line with empirical studies, e.g.,
\citep{Vlachos2021}\comment[id=HM]{Need a back-of the envelope calculation} To use
another metric, the effective weekly reproduction number differs by $0.018$ and $0.052$,
respectively. In light of the large negative effects school closures have on children
and parents \citep{Luijten2021, Melegari2021}---and in particular on those with low
socio-economic status---these results in conjunction with hindsight bias suggest that
opening schools combined with a testing strategy would have been beneficial. In other
situations, and particular when rapid test are not available at scale, trade-offs may
well be different.

>>>>

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December onwards. Some states started
opening them gradually in late February, but operation at normal capacity did not resume
until the beginning of June. Figure~\ref{fig:school_scenarios} shows the effects of
different policies regarding school starting at Easter, at which point rapid tests had
become widely available. We estimate the realized scenario to have essentially the same
effect as a situation with closed schools. Under fully opened schools with mandatory
tests, total infections would have been 6\% higher; this number rises to 20\% without
tests. These effect sizes are broadly in line with empirical studies
\citep[e.g.,][]{Vlachos2021}. \comment[id=HM]{Need a back-of the envelope calculation} To use
another metric, the effective weekly reproduction number differs by $0.018$ and $0.052$,
respectively. In light of the large negative effects school closures have on children
and parents \citep{Luijten2021, Melegari2021}---and in particular on those with low
socio-economic status---these results in conjunction with hindsight bias suggest that
opening schools combined with a testing strategy would have been beneficial. In other
situations, and particular when rapid test are not available at scale, trade-offs may
well be different.
